\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{tabularx, multirow, multicol, graphicx, helvet, siunitx, pgfplots, xcolor, colortbl}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\arraystretch}{1.5}
\begin{document}

% ---------- CORPORATE HEADER ----------
\begin{tabularx}{\textwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline
\textbf{Materials \& Metallurgy Group} & \textbf{Material Specification 817M40 (EN24)} & \textbf{CRM/MS/01} \\
\hline
\multicolumn{3}{|c|}{\textbf{Page 1 of 3}} \\
\hline
\end{tabularx}

% ---------- SECTION 1 ----------
\vspace{1.5em}\noindent\textbf{\large 1. Overview}\vspace{0.5em}

This standard prescribes the specifications and technical supply conditions of steel 817M40 (EN24). The conditions prescribed here are required to be satisfied by the supplier.

% ---------- SECTION 2 ----------
\vspace{1.5em}\noindent\textbf{\large 2. Equivalent Specifications}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|l|X|}
\hline
\rowcolor{gray!20} \textbf{Equivalent Spec.} & \textbf{Value} \\ \hline
817M40 (EN24) & Green \& Red = 40Ni6Cr4Mo3 \\ \hline
817M40 (EN24) & Green \& Red = 817M40 (EN24) \\ \hline
817M40 (EN24) & Green \& Red = 36CrNiMo4 \\ \hline
817M40 (EN24) & Green \& Red = SNCM8 \\ \hline
817M40 (EN24) & Green \& Red = 4340 \\ \hline
817M40 (EN24) & Green \& Red = IS : 11185 \\ \hline
817M40 (EN24) & Green \& Red = PD 970-2005 \\ \hline
817M40 (EN24) & Green \& Red = DIN \\ \hline
817M40 (EN24) & Green \& Red = JIS \\ \hline
817M40 (EN24) & Green \& Red = AISI \\ \hline
\end{tabularx}

% ---------- SECTION 3 ----------
\vspace{1.5em}\noindent\textbf{\large 3. Chemical Composition Limits}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|l|c|c|}
\hline
\rowcolor{gray!20} \textbf{Element} & \textbf{Minimum} & \textbf{Maximum} \\ \hline
C & 0.36 & 0.44 \\ \hline
Si & 0.10 & 0.35 \\ \hline
Mn & 0.45 & 0.70 \\ \hline
P &  & 0.035 \\ \hline
S &  & 0.035 \\ \hline
 &  & 1.40 \\ \hline
Ni & 1.30 & 1.70 \\ \hline
Mo & 0.20 & 0.35 \\ \hline
Others &  &  \\ \hline
\end{tabularx}

% ---------- SECTION 4 ----------
\vspace{1.5em}\noindent\textbf{\large 4. Hardness as Supplied}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|l|l|}
\hline
\rowcolor{gray!20} \textbf{Min} & \textbf{Max} \\ \hline
180HBS & 230HBS \\ \hline
\end{tabularx}

% ---------- SECTION 5 ----------
\vspace{1.5em}\noindent\textbf{\large 5. Austenite Grain Size (IS 2853/ASTM E112)}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|c|c|}
\hline
\rowcolor{gray!20} \textbf{Item} & \textbf{Grain Size} \\ \hline
1 & 5-8 \\ \hline
2 & 5-8 \\ \hline
3 & 5-8 \\ \hline
4 & 5-8 \\ \hline
5 & 5-8 \\ \hline
\end{tabularx}

% ---------- SECTION 6 ----------
\vspace{1.5em}\noindent\textbf{\large 6. Inclusion Rating (AS 4163/ASTM E45) - Thin Series}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|c|c|}
\hline
\rowcolor{gray!20} \textbf{Item} & \textbf{Rating} \\ \hline
1 & Thin Series \\ \hline
2 & ЗА \\ \hline
3 & 3В \\ \hline
4 & 3C \\ \hline
5 & 3D \\ \hline
\end{tabularx}

% ---------- SECTION 7 ----------
\vspace{1.5em}\noindent\textbf{\large 7. Inclusion Rating (AS 4163/ASTM E45) - Thick Series}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|c|c|}
\hline
\rowcolor{gray!20} \textbf{Item} & \textbf{Rating} \\ \hline
1 & Thick Series \\ \hline
2 & 2A \\ \hline
3 & 2B \\ \hline
4 & 2C \\ \hline
5 & 2D \\ \hline
\end{tabularx}

% ---------- SECTION 8 ----------
\vspace{1.5em}\noindent\textbf{\large 8. Micro Structure (IS ASTM E407)}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|c|X|}
\hline
\rowcolor{gray!20} \textbf{Item} & \textbf{Description} \\ \hline
1 & Uniformly Distributed ferrite \& pearlite should be free from harmful bands Max. Limit for banding shall be 0.050 mm. In case of doubt, results from measurement method should be considered as final. \\ \hline
2 & Uniformly Distributed ferrite \& pearlite should be free from harmful bands Max. Limit for banding shall be 0.050 mm. In case of doubt, results from measurement method should be considered as final. \\ \hline
3 & Uniformly Distributed ferrite \& pearlite should be free from harmful bands Max. Limit for banding shall be 0.050 mm. In case of doubt, results from measurement method should be considered as final. \\ \hline
4 & Uniformly Distributed ferrite \& pearlite should be free from harmful bands Max. Limit for banding shall be 0.050 mm. In case of doubt, results from measurement method should be considered as final. \\ \hline
5 & Uniformly Distributed ferrite \& pearlite should be free from harmful bands Max. Limit for banding shall be 0.050 mm. In case of doubt, results from measurement method should be considered as final. \\ \hline
\end{tabularx}

% ---------- SECTION 9 ----------
\vspace{1.5em}\noindent\textbf{\large 9. Freedom from Defects (IS:11371)}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|c|X|}
\hline
\rowcolor{gray!20} \textbf{Item} & \textbf{Description} \\ \hline
1 & Shall be free from internal \& external surface defects when tested by physical inspection, ultrasonic method \& macro etch method. Shall be free from surface cracks, seams \& laps, harmful porosity, slag, inclusion, harmful dendritic structure, segregation \& cracks. \\ \hline
2 & Shall be free from internal \& external surface defects when tested by physical inspection, ultrasonic method \& macro etch method. Shall be free from surface cracks, seams \& laps, harmful porosity, slag, inclusion, harmful dendritic structure, segregation \& cracks. \\ \hline
3 & Shall be free from internal \& external surface defects when tested by physical inspection, ultrasonic method \& macro etch method. Shall be free from surface cracks, seams \& laps, harmful porosity, slag, inclusion, harmful dendritic structure, segregation \& cracks. \\ \hline
4 & Shall be free from internal \& external surface defects when tested by physical inspection, ultrasonic method \& macro etch method. Shall be free from surface cracks, seams \& laps, harmful porosity, slag, inclusion, harmful dendritic structure, segregation \& cracks. \\ \hline
5 & Shall be free from internal \& external surface defects when tested by physical inspection, ultrasonic method \& macro etch method. Shall be free from surface cracks, seams \& laps, harmful porosity, slag, inclusion, harmful dendritic structure, segregation \& cracks. \\ \hline
\end{tabularx}

% ---------- SECTION 10 ----------
\vspace{1.5em}\noindent\textbf{\large 10. Depth of Decarburization (IS:6396)}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|c|X|}
\hline
\rowcolor{gray!20} \textbf{Item} & \textbf{Description} \\ \hline
1 & Depth of decarburization when measured in accordance with IS:6396 or any other method shall not exceed the limit given in table 6 to 8 as in IS:11185. \\ \hline
2 & Depth of decarburization when measured in accordance with IS:6396 or any other method shall not exceed the limit given in table 6 to 8 as in IS:11185. \\ \hline
3 & Depth of decarburization when measured in accordance with IS:6396 or any other method shall not exceed the limit given in table 6 to 8 as in IS:11185. \\ \hline
4 & Depth of decarburization when measured in accordance with IS:6396 and any other method shall not exceed the limit given in table 6 to 8 as in IS:11185. \\ \hline
5 & Depth of decarburization when measured in accordance with IS:6396 or any other method shall not exceed the limit given in table 6 to 8 as in IS:11185. \\ \hline
\end{tabularx}

% ---------- SECTION 11 ----------
\vspace{1.5em}\noindent\textbf{\large 11. Heat Treatment Condition as Supplied}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|c|X|}
\hline
\rowcolor{gray!20} \textbf{Item} & \textbf{Condition} \\ \hline
1 & Annealed / Normalized as hot rolled or forged. \\ \hline
2 & Annealed / Normalized as hot rolled or forged. \\ \hline
3 & Annealed / Normalized as hot rolled or forged. \\ \hline
4 & Annealed / Normalized as hot rolled or forged. \\ \hline
5 & Annealed / Normalized as hot rolled or forged. \\ \hline
\end{tabularx}

% ---------- SECTION 12 ----------
\vspace{1.5em}\noindent\textbf{\large 12. Surface Condition as Supplied}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|c|c|}
\hline
\rowcolor{gray!20} \textbf{Item} & \textbf{Condition} \\ \hline
1 & Black \\ \hline
2 & Black \\ \hline
3 & Black \\ \hline
4 & Black \\ \hline
5 & Black \\ \hline
\end{tabularx}

% ---------- SECTION 13 ----------
\vspace{1.5em}\noindent\textbf{\large 13. Test Certificate}\vspace{0.5em}

\begin{tabularx}{\textwidth}{|c|X|}
\hline
\rowcolor{gray!20} \textbf{Item} & \textbf{Requirement} \\ \hline
1 & Test certificate shall be provided by the supplier for all specified chemical. \\ \hline
2 & Test certificate shall be provided by the supplier for all specified chemical. \\ \hline
3 & Test certificate shall be provided by the supplier for all specified chemical. \\ \hline
4 & Test certificate shall be provided by the supplier for all specified chemical. \\ \hline
5 & Test certificate shall be provided by the supplier for all specified chemical. \\ \hline
\end{tabularx}

% ---------- SECTION 14 ----------
\vspace{1.5em}\noindent\textbf{\large 14. Miscellaneous}\vspace{0.5em}

an Ale a name aliasa English (United Kingdom) * Adobe Acrobat| D Focus TCS -1.17\% \textasciicircum{}

\end{document